There once was a grid at ol' Carkeek

### 2016-08-13 Manuscript/v0.0/carkeek_grid.tex
add DNA purification

\subsection*{Laboratory Procedures}

Samples were randomly assigned to PCR primer and library adapter index sequences.
The sequencing run consisted of 14 samples ('libraries') prepared using different index sequences ligated during library preparation.
Of these libraries, ten comprised of amplicons prepared using the 16S protocol reported above, and four comprised of amplicons prepared using a 12S protocol similar to that reported by (CITE PORT 2015).

>>>>

\subsection*{DNA Purification}

DNA was purified from the membrane following a phenol:chloroform:isoamyl alcohol protocol similar to Renshaw (CITE RENSHAW).
Preserved membranes were incubated at 65C for 30 minutes before adding 900 microliters of phenol:chloroform:isoamyl alcohol and shaking vigorously for 60 seconds.
We conducted two consecutive chloroform washes by centrifuging at 14,000 rpm for 5 minutes, transferring the aqueous layer to 700 microliters chloroform, and shaking vigorously for 60 seconds.
After a third centrifugation, 500 microliters of the aqueous layer was transferred to tubes containing 20 microliters 5 molar NaCl and 500 microliters 100\% isopropanol, and frozen at -20C for approximately 15 hours.
Finally, all liquid was removed by centrifuging at 14000 rpm for 10 minutes, pouring off or pipetting out any remaining liquid, and drying in a vacuum centrifuge at 45C for 15 minutes.
DNA was resuspended in 200 microliters of ultrapure water.
Genomic DNA extracted from tissue of a species absent from the sampled environment (Struthio camelus) served as positive control for the remaining protocols.
